### 2024-10-29 paper/3-motivation.tex
Fix explanation related to enter

Example 2 is a WebAssembly code example that has \texttt{loop} whose block is
only \texttt{i32.const}, and \texttt{f32.const}
When the \texttt{loop} instruction is executed, a label is pushed in the stack,
and it enters the block.
After \texttt{i32.const} is executed, the end of the block is reached.
As a result, exiting label occurs so that the label is popped from the stack,
pc changes to the point after the end of block: \texttt{f64.const}.
As a result, after executing the code, the value 42 and 3.14 pushed to the
stack.

@@

Consider example 1 above.
If we assume some control structure $c^*$ is given, the code can be expressed
like \cref{eq:loop-1}.
\cref{fig:spectec-loop} is the \spectecp{} of the \texttt{loop} instruction.
Rather than storing the point to jump as a continuation in the label, it stores
the \texttt{loop} instruction itself and \textit{enters} the block.
Here, \textit{enter} means that it pushes the label in the stack and executes
the instructions in the block, which means that \texttt{i32.const},
\texttt{br}, \texttt{unreachable}, \texttt{end} and \texttt{unreachable} become
the new inputs in \cref{eq:loop-2}.
When \texttt{i32.const} is excuted, it pushes 42 as \officialp{} does
in \cref{eq:loop-3}.
The value is omitted for brevity.
However, \texttt{br} behaves a bit differently.
\cref{fig:spectec-br} is the \spectecp{} of the \texttt{br} instruction.
It pops the label from the stack, removes the input instructions until the end
of the block, considers the loop instruction in the label as a new input
instruction.
Consequently, remaining inputs are \texttt{loop}, and \texttt{unreachable}
again in \cref{eq:loop-4}.
Therefore, it explains the same behavior in a different point of view.

@@

Example 3 contains a function definition whose body is \texttt{i32.const}, a
\texttt{call} instruction followed by a \texttt{f32.const} instruction, which
can be expressed in \cref{eq:call-1}.
By invoking a function, it enters the block in \cref{eq:call-2}.
After executing the body in \cref{eq:call-3}, an \texttt{end} is executed.
In this point, this \texttt{end} represent both the end of the block and the
function.
As a consequence, this \text{end} perform both exiting label and returning from
a function in \cref{eq:call-4}, and the instruction after the \texttt{call} is
executed in \cref{eq:call-5}
It results in the values 42 and 3.14 pushed to the stack.

>>>>

Example 2 is a WebAssembly code example that has \texttt{loop} whose block is
only \texttt{i32.const}, and \texttt{f32.const}
When the \texttt{loop} instruction is executed, it enters the block with a label.
After \texttt{i32.const} is executed, the end of the block is reached.
As a result, exiting label occurs so that the label is popped from the stack,
pc changes to the point after the end of block: \texttt{f64.const}.
As a result, after executing the code, the value 42 and 3.14 pushed to the
stack.

@@

Consider example 1 above.
If we assume some control structure $c^*$ is given, the code can be expressed
like \cref{eq:loop-1}.
\cref{fig:spectec-loop} is the \spectecp{} of the \texttt{loop} instruction.
Rather than storing the point to jump as a continuation in the label, it stores
the \texttt{loop} instruction itself in the label, and \textit{enters} the
block.
Here, \textit{enter} means that it pushes the label in the stack and executes
the instructions in the block, which means that \texttt{i32.const},
\texttt{br}, \texttt{unreachable}, \texttt{end} and \texttt{unreachable} become
the new inputs in \cref{eq:loop-2}.
When \texttt{i32.const} is excuted, it pushes 42 as \officialp{} does
in \cref{eq:loop-3}.
The value is omitted for brevity.
However, \texttt{br} behaves a bit differently.
\cref{fig:spectec-br} is the \spectecp{} of the \texttt{br} instruction.
It pops the label from the stack, removes the input instructions until the end
of the block, considers the loop instruction in the label as a new input
instruction.
Consequently, remaining inputs are \texttt{loop}, and \texttt{unreachable}
again in \cref{eq:loop-4}.
Therefore, it explains the same behavior in a different point of view.

@@

Example 3 contains a function definition whose body is \texttt{i32.const}, a
\texttt{call} instruction followed by a \texttt{f32.const} instruction, which
can be expressed in \cref{eq:call-1}.
By invoking a function, it pushes a frame and enters the block with a label in
\cref{eq:call-2}.
After executing the body in \cref{eq:call-3}, an \texttt{end} is executed.
In this point, this \texttt{end} represent both the end of the block and the
function.
As a consequence, this \text{end} perform both exiting label and returning from
a function in \cref{eq:call-4}, and the instruction after the \texttt{call} is
executed in \cref{eq:call-5}
It results in the values 42 and 3.14 pushed to the stack.
